$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-05-11 paper/e6ssm-tuning-paper.tex
Changed wording to address referee point 6

Here we will focus most on the special case where the gauge symmetry
is $U(1)_N$, under which the right handed neutrino $\hat{N}^c$ remains
interaction-less.  This is the case in the E$_6$SSM \cite{King:2005jy,
King:2005my, Athron:2010zz}, and closely-related variants \cite{Howl:2007zi,
Braam:2009fi, Braam:2010sy, Hall:2011zq, Nevzorov:2012hs, Athron:2014pua}.
Since the right handed neutrino has no gauge symmetry protecting it's mass
from becoming extremely heavy such models may explain the tiny observed
masses of neutrinos via the see-saw mechanism and the baryon asymmetry in
the universe via leptogenesis \cite{Hambye:2000bn, King:2008qb, King:2008gw}.
Recently it has also been studied in the context of electroweak baryogenesis
\cite{Chao:2014hya}.

>>>>

Here we will focus most on the special case where the gauge symmetry
is $U(1)_N$, under which the right handed neutrino $\hat{N}^c$ does not
participate in gauge interactions.  This is the case in the E$_6$SSM
\cite{King:2005jy, King:2005my, Athron:2010zz}, and closely-related variants
\cite{Howl:2007zi, Braam:2009fi, Braam:2010sy, Hall:2011zq, Nevzorov:2012hs,
Athron:2014pua}.  Since the right handed neutrino has no gauge symmetry
protecting it's mass from becoming extremely heavy such models may explain
the tiny observed masses of neutrinos via the see-saw mechanism and the
baryon asymmetry in the universe via leptogenesis \cite{Hambye:2000bn,
King:2008qb, King:2008gw}.  Recently it has also been studied in the context
of electroweak baryogenesis \cite{Chao:2014hya}.
